---
title: "HW5 notebook"
output:
  html_document:
    df_print: paged
---

Here is the first method for overlaying shape data on a raster.

Use the following packages (install them first), then use them via
the library() call: tmap, tmaptools, rgdal, sp, OpenStreetMap, osmdata

These calls are useful: readOGR(), tmaptools::read_osm(),
tm_shape(), tm_raster(), tm_dots()

1. readOGR() your shapefile, store it in a var
2. read_osm() the bbox of #1 above, store it in a var
3. do tm_shape() on #2 + tm_raster() +
tm_shape() on #1 + tm_dots() to specify point color and size

```{r}
library(tmap)
library(tmaptools)
library(rgdal)
library(rJava)
library(sp)
library(OpenStreetMap)
library(osmdata)


myObject<-readOGR("./mygeodata","spatial")
bb<-read_osm(myObject@bbox)
tm_shape(bb)+tm_raster()+tm_shape(myObject)+tm_dots("red",size=.5)

```

And here's the second.

Use these packages: PBSmapping, ggmap
And these calls: importShapefile(), as.data.frame(), get_map(), ggmap(), 
geom_point()

1. importShapefile() into a var
2. convert it (#1 above) to a dataframe, store it in a var
3. get_map() with a location that's in your collection of (lat,long),
store it in a var
4. do ggmap() on #3, + geom_point() on #2

```{r}
library(PBSmapping)
library(ggmap)

spatial.pb <- importShapefile("mygeodata/spatial")
df <- as.data.frame(spatial.pb)
sp_map<-get_map(location=c(-118.2846,34.022),maptype="roadmap", source = "google", zoom = 13)
ggmap(sp_map)+geom_point(data=df,aes(x=X, y=Y),color="red")
```


